---
title: "Weight of Fish"
author: "Jocelyn Lazcano"
date: "SPRING 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```


```{r}
Fishdata=read.csv(file="Fish.csv")
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables 

# PERCH

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Perchdata=filter(Fishdata, Species=="Perch")
Perchdata = subset (Perchdata, select = -Species)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perchdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

The best model uses the variable height and width. 

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perchdata)
fullup <- lm(Weight~.,data = Perchdata)
summary(best.model)
```
The P- value here is so small, that it actually shows that this model is an excellent fit. 


```{r}
anova(fullup,best.model)
```

The P-value is 0.879 which means that there is not a significant difference between using all the model that has all of them vs. the model that only uses 2 variables. 

# BREAM

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Breamdata=filter(Fishdata, Species=="Bream")
Breamdata = subset (Breamdata, select = -Species)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Breamdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

  
## Which is best??  

The best model is the one that uses three variables length, height and width. 

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[3,]
```


```{r}
best.model <- lm(Weight~Length2+Height,data=Breamdata)
fullup <- lm(Weight~.,data = Breamdata)
summary(best.model)
```


```{r}
anova(fullup,best.model)
```

The P-value is too large to say that there is a difference between using the best model which utilizes three varaibles and the best model that utilizes the two. 


# SMELT

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Smeltdata=filter(Fishdata, Species=="Smelt")
Smeltdata = subset (Smeltdata, select = -Species)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smeltdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

## Which is best??  

The best model is the one that uses the 4 variables Length1, Length2, height and width.

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[3,]
```


```{r}
best.model <- lm(Weight~Length2+Width,data=Smeltdata)
fullup <- lm(Weight~.,data = Smeltdata)
summary(best.model)
```


```{r}
anova(fullup,best.model)
```

The P-value is too large to determine if there is a difference between the best model that use 4 variables and the best model that uses two variables. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


Based on the automated selection of variables there is no real difference in using a model with two variables vs. using one with with all of the variables. This was identified through a graphical description of the adjusted rsquared as well as the pvalues. In conclusion, comparing the pvalues of the two variable models the pvalues are so small that we reject the null hypothesis that these models are able to predict the weight of fish. The pvalues that are also associated with anovas are so large we fail to reject the null hypothesis. There is no difference between using the model with two variables vs. the full up models. 

